Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-02-19 index.qmd
update
feat: high ts Juno processing

>>>>

### 02/19/2024

{{< embed notebooks/04_properties.ipynb#fig-jno-8hz-tau-20-der >}}

### 02/18/2024

![](figures/new/duration/duration_dist_ts_comparison)

#### Thickness
::: {.column-screen layout-nrow="1"}
![](figures/new/thickness/thickness_k_dist)

![](figures/new/thickness/thickness_k_dist-8hz)

![](figures/new/thickness/thickness_k_dist-8hz-tau_20)
:::

#### Current Density

::: {.column-screen layout-nrow="1"}
![](figures/new/current/current_k_dist)

![](figures/new/current/current_k_dist-8hz)

![](figures/new/current/current_k_dist-8hz-tau_20)

### 02/17/2024

![](figures/new/duration/duration_dist)

![](figures/new/thickness/thickness_k_fit_dist)

![](figures/new/current/current_k_dist)
:::
